# plotr

<!-- quarto render -->

```{r}
#| label: setup
#| include: false

library(plotr)

# Related to './R/.post-render.R'
library(beepr)
library(cffr)
library(codemetar)
library(groomr) # https://github.com/danielvartan/groomr
library(here)
library(readr)
library(rutils) # https://github.com/danielvartan/rutils
library(stringr)
```

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check.yaml](https://github.com/danielvartan/plotr/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/danielvartan/plotr/actions/workflows/check-standard.yaml)
[![Codecov test coverage](https://codecov.io/gh/danielvartan/plotr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/danielvartan/plotr?branch=main)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](CODE_OF_CONDUCT.md)
<!-- badges: end -->

## Overview

`plotr` is an R package designed to provide quick and easy access to commonly used plotting functions in data analysis.

## Installation

You can install `plotr` using the [`remotes`](https://github.com/r-lib/remotes) package:

``` {r}
#| eval: false

remotes::install_github("danielvartan/plotr")
```

## License

[![License:
MIT](https://img.shields.io/badge/license-MIT-green)](https://opensource.org/license/mit)

`plotr` code is released under the [MIT license](https://opensource.org/license/mit).

## Contributing

Contributions are welcome, including bug reports. Take a moment to review the [Guidelines for Contributing](https://danielvartan.github.io/plotr/CONTRIBUTING.html).

<br>

Become an `plotr` supporter!

Click [here](https://github.com/sponsors/danielvartan) to make a donation. Please indicate the `plotr` package in your donation message.
